Hypertension and microbiome

### 2019-01-23 articletwo.Rmd
Bugs at atlas

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, xecho = TRUE, message = FALSE, results='asis', cache=TRUE, warning=FALSE)
knitr::opts_chunk$set(cache.path = 'cache/', output.dir="cache/",
                      file.path = 'cache/', fig.path = 'cache/')

@@

```{r Officer importer, code=readLines("articleone-officer.R")}
source("articletwo-officer.R")
```

@@

beta.diversity <- adonis.species %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"))

                                        #%>%
    dplyr::select(response, R2)

@@

plot.gtable.beta.diversity <- ggplot_gtable(ggplot_build(plot.beta.diversity))
plot.xlab.beta.diversity <- xlabb_extractor(gtable.beta.diversity)

@@

```{r Main contributors of PC3}
pca.loading <- pca.prcomp$rotation^2 %>%
    as.data.frame %>%
    tibble::rownames_to_column(var = "term") %>%
    mutate(name = rename.genus(term))

@@

```{r Write docx to file, cache = FALSE, results = FALSE, include = FALSE}
print(doc, target = paste0("report/articletwo-", now, ".docx"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, xecho = TRUE, message = FALSE, results='asis', cache=FALSE, warning=FALSE)
knitr::opts_chunk$set(cache.path = 'cache/', output.dir="cache/",
                      file.path = 'cache/', fig.path = 'cache/')

@@

```{r Officer importer, code=readLines("articletwo-officer.R")}
source("articletwo-officer.R")
```

@@

beta.diversity <- adonis.species %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")) %>%
    dplyr::select(response, R2)

@@

plot.gtable.beta.diversity <- ggplot_gtable(ggplot_build(plot.beta.diversity))
plot.xlab.beta.diversity <- xlabb_extractor(plot.gtable.beta.diversity)

@@

```{r Main contributors of PC3}
pca.rotation.abs <- abs(pca.prcomp$rotation)
pca.loading <- sweep(pca.rotation.abs, 2, colSums(pca.rotation.abs), "/") %>%
	    as.data.frame %>%
    tibble::rownames_to_column(var = "term") %>%
    mutate(name = rename.genus(term))

@@

```{r Write docx to file}
print(doc, target = paste0("report/articletwo-", now, ".docx"))
```
